Centralizers of higher enveloping algebras of Lie algebras

### 2020-01-28 draft.tex
some rearrangment

Some easy but important situations to examine:
\begin{itemize}
\item When $n=0$, we see naive endomorphisms arise.
\item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $E_n$ HKR theorem.
\item Compare with $E_n$ HKR theorem for $\clies(\fg)$ via $E_n$ Koszul duality.
\item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
\end{itemize}

@@

For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
see Example \ref{eg: TT}.

\begin{rmk}
The preceding results are quick consequences of published work and are well-known to experts we spoke to, including John Francis and Ben Knudsen. 
Nevertheless, we record these results so they are documented in the literature.
\end{rmk}

@@

\begin{thm}
\label{thm: large N}

The centralizer ${\frak Z}_{E_n}(\UU_nu_A)$ of the map $\UU_nu_A$ is the $E_n$ algebra obtained by forgetting the dg commutative algebra
\[
\clies(\sl_\infty(k)) \otimes \Sym(\Cyc_*(A)[1-n])
\]
down to an $E_n$ algebra.

@@

\greg{need to add a notation/convention somewhere including that $\Sigma^n$ will be shift functor, convention for grading and so on}
\section{Enveloping $E_n$ algebras of Lie algebras}

@@

The second part of this result leads to the explicit models in our theorems.
Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}. 
\begin{thm}\label{T:En=Fac} there is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant factorization algebras.
\end{thm}
\begin{rmk}
 It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to 
 $\Sigma^{n-1}B = B[n-1]$. Henceforth in this paper, we will simply use the notation  $B[n-1]$ for $\oblv_n(B)$, that is tacitly assume 
 $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
\end{rmk}

Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
$\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}$
gives a $L_\infty$-algebra morphism 
\begin{equation}
 \tilde{f}: \fg \, \longrightarrow \, \oblv(B)\cong B[n-1]
\end{equation}
which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.
\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. The induced  
 $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in $\fg$-module. 
\end{prp}
\begin{proof}

@@

\medskip

@@

@@

>>>>

Some easy but important situations to examine:
\begin{itemize}
\item When $n=0$, we see naive endomorphisms arise.
\item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
\item When $n=1$, unpack in detail how the convolution picture matches the classic view of Koszul duality for associative (co)algebras.
\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $E_n$ HKR theorem.
\item Compare with $E_n$ HKR theorem for $\clies(\fg)$ via $E_n$ Koszul duality.
\item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
\end{itemize}

@@

For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
see Example~\ref{eg: TT}.

\begin{rmk}
The preceding results are known to experts we spoke to, including John Francis and Ben Knudsen. 
Nevertheless, we record these results to document in the literature and for future use in mathematical physics,
where such constructions already appear but lack proofs of their universal properties.
\end{rmk}

\owen{Below is an orphaned set of results. Perhaps we prove it, or perhaps we just reserve it for future projects.}

@@

\begin{thm}
\label{thm: large N}
The centralizer ${\frak Z}_{E_n}(\UU_nu_A)$ of the map $\UU_nu_A$ is the $E_n$ algebra obtained by forgetting the dg commutative algebra
\[
\clies(\sl_\infty(k)) \otimes \Sym(\Cyc_*(A)[1-n])
\]
down to an $E_n$ algebra.

@@

\greg{need to add a notation/convention somewhere including that $\Sigma^n$ will be shift functor, convention for grading and so on}

\section{Enveloping $E_n$ algebras of Lie algebras}

@@

The second part of this result leads to the explicit models in our theorems.
Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.

\begin{thm}
\label{T:En=Fac} 
There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant factorization algebras.
\end{thm}

\begin{rmk}
 It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to 
 $\Sigma^{n-1}B = B[n-1]$. Henceforth in this paper, we will simply use the notation  $B[n-1]$ for $\oblv_n(B)$, that is tacitly assume 
 $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
\end{rmk}

\owen{I'm not wild about Greg's phrasing below. Also, I'd prefer to move the explicit formulas later, when we've shifted our setting to strict prefactorization algebras.}

Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
\[
\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}
\]
gives a $L_\infty$-algebra morphism 
\begin{equation}
 \tilde{f}: \fg \, \longrightarrow \, \oblv(B)\cong B[n-1]
\end{equation}
which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.
\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. The induced  
 $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in $\fg$-module. 
\end{prp}
\begin{proof}

@@

@@

\section{Convolution algebras over colored operads}

\def\conv{{\rm Conv}}

\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}

\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^! \to A$ from $C^! = \conv(C,1)$, the ``Koszul dual'' $\cO$-algebra to the coalgebra $C$. This cocycle can be used to twist the differential of $\conv(C,A)$. Hopefully this admits an obvious deformation-theoretic interpretation.}

\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}

@@

\section{Leftover stuff}

\owen{I took the following out of Greg's version of the "main theorem" section}
